---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/kota7/rddsigma.svg?branch=master)](https://travis-ci.org/kota7/rddsigma)

# rddsigma
Sharp Regression Discontinuity Design with Running Variable Measured with Error 


This package provides estimators for the standard deviation of measurement errors
in running variables for sharp regression discontinuity designs.
The estimation requires the data for observed (mismeasured) running variables and 
assigment variables. 


## Installation

Install from GitHub using `devtools::install_github` function.

```r
devtools::install_github("kota7/rddsigma")
```


## Quick Start

Use `estimate_sigma` function.
```{r}
library(rddsigma)
set.seed(875)

# generate simulation data
dat <- gen_data(500, 0.3, 0)

estimate_sigma(dat$d, dat$w, cutoff=0)
```


## Estimation Methods

The package support two estimators for estimating `sigma`.
The first estimator assumes that both the true runnning variable and the measurement error
follow the Gaussian distribution.
This is the default estimator of `estimate_sigma` function, or specified explicitly by
setting `method="tsgauss"`

```{r}
estimate_sigma(dat$d, dat$w, cutoff=0, method="tsgauss")
```


The second estimator relaxes the Gaussian assumption and allows 
the true runnning variable and the measurement error to follow some parametric distribution.
Currently, the package supports the Gaussian distribution for the running variable and the Gaussian and Laplace distributions for the measurement error.
This estimator is called with `method="emparam"`
```{r}
estimate_sigma(dat$d, dat$w, cutoff=0, method="emparam", x_dist="gauss", u_dist="gauss")
estimate_sigma(dat$d, dat$w, cutoff=0, method="emparam", x_dist="gauss", u_dist="lap")
```

